Spatial variation of coronal Fourier power spectra

### 2016-02-03 tex/paper2/paper2.tex
adding in how to estimate the power law index in a power law power spectrum; working on adding in how the spectra are estimated

\shorttitle{Coronal Fourier power spectra}
\shortauthors{Ireland et al.}

@@

\begin{abstract}

  {\BF The dynamics of regions of the solar corona are investigated
    using {\BF Atmospheric Imaging Assembly (AIA)} 171\AA\ and
    193\AA\ data.  The coronal emission from the quiet Sun, coronal
    loop footprints, coronal moss, and from above a sunspot is
    studied.  It is shown that the \mFpa\ in these regions can be
    described by a \PL\ at lower frequencies that tails to flat
    spectrum at higher frequencies, plus a Gaussian-shaped
    contribution that varies depending on the region studied. This
    Fourier spectral shape is in contrast to the commonly-held
    assumption that coronal time-series are well described by the sum
    of a long time-scale background trend plus Gaussian-distributed
    noise, with some specific locations also showing an oscillatory
    signal.  The implications of this discovery to the field of
    coronal seismology and the automated detections of oscillations
    are discussed.  The \PL\ contribution to the shape of the Fourier
    power spectrum is interpreted as being due to the summation of a
    distribution of exponentially decaying emission events along the
    line of sight.}  This is consistent with the idea that the solar
  atmosphere is heated everywhere by small energy deposition events.
\end{abstract}

@@

Models are fit by first generating an estimate of the model
parameters.  This estimate is used as an initial guess to a fitting
routine.  Models were fit by varying model parameters to find the
maximum of the log of likelihood of the data given the model.  The
Nelder-Mead method was used to vary model parameters in search of the
maximum of the log likelihood.

The initial guess for model \ref{eqn:} is generated as follows.  An
estimated power law index

@@

>>>>

\shorttitle{Spatial variation of coronal Fourier power spectra}
\shortauthors{Ireland et al.}

@@

\begin{abstract}
The dynamics of the solar corona are investigated using data from the
six extreme ultraviolet channels (EUV) of the  Atmospheric Imaging
Assembly (AIA) of the Solar Dynamics Observatory (SDO).

It is shown that in almost all locations the \Fps\ are well be described by
a \PL\ at lower frequencies that tails to flat spectrum at higher
frequencies, plus a Gaussian-shaped contribution that varies depending
on the region studied.

\end{abstract}

@@

\Fpa\ models are fit by first generating an estimate of the model
parameters.  This estimate is used as an initial guess to a fitting
routine.

Models were fit by varying model parameters to find the
maximum of the log of likelihood of the data given the model.

Fourier power components are exponentially distributed.  Let us assume
that $I_{j}$ is the observed Fourier power at the frequency indexed by
$j$, and $S_{j}$ is the model Fourier power at that same frequency.
The probability of an observed power $I_{j}$ given a model power
$S_{j}$ is given by
\begin{equation}
p_{j}\left(I_{j}|S_{j}\right) =
\frac{1}{S_{j}}\exp\left[-\frac{I_{j}}{S_{j}}\right]
\label{eqn:freqprob}
\end{equation}
If there are $N$ non-zero Fourier frequencies then the likelihood over
all frequencies is
\begin{equation}
L=\prod_{j=1}^{N}p\left(I_{j}|S_{j}\right)
\label{eqn:freqprob:all}
\end{equation}
The
Nelder-Mead method was used to vary model parameters in search of the
maximum of the log likelihood.

The initial guess for model \ref{eqn:} is generated as follows.  An
estimated power law index is

@@

\subsection{Estimating the power-law index in a power law power
  spectrum}\sec{sec:app:est}
Equation \ref{eqn:freqprob:all} describes the likelihood of the
observed Fourier power given a model for that power.  We assume that
the observed power law spectrum can be modeled by a simple power law
over all frequencies
\begin{equation}
S_{j} = Af_{j}^{-n}
\end{equation}
where $A$ is a constant, $f_{j}$ is the $j$'th Fourier frequency, and
$n$ is the power law index we wish to estimate.  An estimate can be
derived using Bayes' theorem. Using the likelihood function derived
above (\ref{eqn:freqprob:all}), and assuming the prior $p(A)\propto
A^{m}$ for some value of $m$, then 
\begin{equation}
p(n) \propto \int_{0}^{\infty} p(A) L dA.
\label{eqn:bayes}
\end{equation}
On integration,
\begin{equation}
\ln p(n) \propto n\sum_{j=1}^{N}\ln f_{j} - (N-m-1)\ln\left[\sum_{j=1}^{N}I_{j}f_{j}
\label{eqn:pnlog}
\end{equation}
For the purposes of this investigation, $m=0$ and an estimate to $n$
was found by finding calculating the value of $\ln p(n)$ in the range
$n=0\rightarrow4$ with steps of 0.01 and finding the value of $n$ that
maximized $\ln p(n)$.
